Hydra Battles in Coq

### 2020-11-08 doc/hydras.tex
correction of typos

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we prove amso in larger notation systems, as well as in Schütte's model.}

>>>>

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we prove also in larger notation systems, as well as in Schütte's model.}
